STAT 450 Project: Real Estate

### 2020-04-14 doc/450/RealEstate_final_report.Rmd
tiny fix

Here categorical variables are taken into account. Boxplots of mill rate across municipalities and tax classes are plotted to display the distributions in **Figure 3** and **Figure 4**, respectively.

>>>>

Here categorical variables are taken into account. Boxplots of mill rate across municipalities and tax classes have been plotted to display the distributions in **Figure 3** and **Figure 4**, respectively.
